Latent Dirichlet Allocation Time Series (LDATS)

### 2020-04-21 doc/LDATS_codebase.Rmd
codebase vignette
updated to the current codebase

* `LDA_TS()`
  * `check_LDA_TS_inputs()`
    * `check_timename()`
    * `check_formulas()`
    * `check_nchangepoints()`
    * `check_weights()`
    * `check_control()`
    * `check_document_term_table()`
    * `check_document_covariate_table()`	
    * `check_topics()`
    * `check_seeds()`
  * `LDA_set()`
    * `check_LDA_TS_inputs()`
      * `check_control()`
      * `check_document_term_table()`
      * `check_topics()`
      * `check_seeds()`
    * loop over models
      * `prep_LDA_control()`
      * `LDA()`
  * `select_LDA()`
    * applies the `measurer` and `selector` functions supplied via `LDA_controls_list()`
  * `TS_on_LDA()`
    * `check_LDA_TS_inputs()`
      * `check_LDA_models()`
      * `check_formulas()`
      * `check_nchangepoints()`
      * `check_timename()`
      * `check_control()`
      * `check_weights()`
      * `check_document_covariate_table()`	
    * `expand_TS()`
    * loop over models
      * `prep_TS_data()`
      * `TS()`
        * `check_TS_inputs()`
          * `check_formulas()`
          * `check_nchangepoints()`
          * `check_control()`
          * `check_weights()`
        * `est_changepoints()`
          * `prep_saves()`
          * `prep_ptMCMC_inputs()`
          * `prep_cpts()`
            * loop over chains
              * `multinom_TS()`
          * `prep_ids()`
          * `prep_pbar()`
          * loop over iterations
            * `update_pbar()`
            * `step_chains()`
              * `propose_step()`
                * `proposed_step_mods()`
                  * loop over chains
                    * `multinom_TS()`
              * `eval_step()`
              * `take_step()`
            * `swap_chains()`
                * loop over chain neighbors
            * `update_saves()`
            * `update_cpts()`
            * `update_ids()`
        * `est_regressors()`
          * loop over unique realizations of change point locations
            * `multinom_TS()`
            * loop over chunks
              * `mirror_vcov()`
              * `rmvnorm()`
        * `summarize_TS()`
          * `diagnose_ptMCMC()`
            * `count_trips()`
          * `summarize_rhos()`
          * `measure_rho_vcov()`
          * `summarize_etas()`
          * `measure_eta_vcov()`
    * `select_TS()`
      * applies the `measurer` and `selector` functions supplied via `TS_controls_list()`
    * `package_LDA_TS()`

Each component model's function (`LDA_set()` and `TS()`) can be run
independently, as well.

@@

To minimize the length of argument lists and facilitate simple default usage
throughout the pipeline, we implement an options/controls list approach, where
each of the main functions (`LDA_TS`, `LDA_set`, and `TS`) has a controls 
list (although `LDA_set` is referenced as `LDA` in the naming scheme)

* `LDA_TS_controls_list()`
* `LDA_controls_list()`
* `TS_controls_list()`

>>>>

* `LDA_TS()`
  * `LDA_TS_control()`
    * `LDA_control()`
    * `TS_control()`
  * `LDA()`
    * `prepare_LDA()`
      * `check_LDA()`
      * `LDA_control()`
      * `conform_data()`
    * `run_LDA()`
      * `LDA_call()` (replicated for each model)
        * `LDA_msg()`
        * `soft_call()` using `LDA$control$model` with `LDA$control$model_args`
          * `topicmodels::LDA()` (*default*) 
      * `package_LDA()`
        * `select_LDA()`
          * `soft_call()` using `LDA$control$selector with LDA$control$selector_args
            * `min()` (*default*) 
            * `measure_LDA()` (replicated for each model)
              * `soft_call()` using `LDA$control$measurer` with `LDA$control$measurer_args`
            * `AIC()` (*default*)

  * `TS()`
    * `prepare_TS()`
      * `TS_control()`
      * `run_TS()`
        * `TS_call()` (replicated for each model)
          * `TS_msg()`
          * `TS$control$model with TS$control$model_args
            * `sequential_TS_control()`
            * `est_changepoints()`
              * `TS$control$method` with `TS$control$method_args`
                * `ldats_classic_control()`
                  * `prep_saves()`
                  * `prep_ptMCMC_inputs()`
                    * `prep_temp_sequence()`
                    * `prep_proposal_dist()`
                  * `prep_cpts()`
                    * `prep_temp_sequence()`
                    * `TS$control$response` with `TS$control$response_args`
                  * `prep_ids()`
                  * `prep_pbar()`
                  * `update_pbar()`
                  * `step_chains()`
                    * `propose_step()`
                      * `proposed_step_mods()`
                      * `TS$control$response` with `TS$control$response_args`
                    * `eval_step()`
                    * `accept_step()`
                  * `swap_chains()`
                  * `update_saves()`
                  * `update_cpts()`
                  * `update_ids()`
                  * `process_saves()`
                    * `count_trips()`
             * `est_regressors()`
               * `TS$control$response` with `TS$control$response_args`
             * `package_sequential_TS()`
               * `summarize_rhos()`
               * `measure_rho_vcov()`
               * `summarize_eta()`
               * `measure_eta_vcov()`
       * `package_TS()`
         * `select_TS()`
           * `TS$control$selector` with `TS$control$selector_args`
           * `measure_TS()` (replicated for each model)
             * `TS$control$measurer` with `TS$control$measurer_args`
  * `package_LDA_TS()`

Each component model's function (`LDA()` and `TS()`) can be run independently, as well.

@@

To minimize the length of argument lists and facilitate simple default usage throughout the pipeline, we implement an options/controls list approach, where each of the main functions (`LDA_TS`, `LDA`, and `TS`) and their subfunctions have a `control` argument that takes a `list` to replace the defaults returned by its `_control` function:

* `LDA_TS_control()`
* `LDA_control()`
* `TS_control()`
